---
title: "PlotlyPresentation"
author: 'N'
date: "September 26, 2018"
output: ioslides_presentation
font_adjustment: -1
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


## London (UK) Crime and Fire Statistics
```{r plotly, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
library(plotly)
plotlyKPIs<-read.csv("C:\\Nick\\07 R\\6JohnHopkins\\9 Developing Data Products\\Week3\\plotlyKPIs.csv")
plot_ly(plotlyKPIs,x=plotlyKPIs$Month, y=plotlyKPIs$totalCrimes_hh,type="scatter",color=plotlyKPIs$Posttown, size=plotlyKPIs$totalFires_hh)
```
<font size="1">Monthly Crime Rates from January 2017 through June 2018:  Monthly Crimes are shown by the bubbles.  Colours denote the different Post Towns of London. Bubble sizes show the equivalent monthly Fire rate per HH per post town.
</font>

## Data and Sources
<font size="1">
The process for producing the data is not provided in a reproducible format due to the requirement for a propriarary UK Map shape file and information on the number of Households present in each UK post sector.  

Some data are in Easting/Northing and need to be projected to Latitude/Longitude (*latlong = "+init=epsg:4326"*) using "spTransform" function.

The UK Shape File is a propriatary shape file (google Superppro data to find the proprioter)
```R63_SuperPro_Postcode_Sectors_SHA.zip```

The data are loaded as Easting/Northing and the .prj file can be obtained as below:
``` OSGB<-"+proj=tmerc +lat_0=49 +lon_0=-2 +k=0.9996012717 +x_0=400000 +y_0=-100000 +ellps=airy +datum=OSGB36 +units=m +no_defs"```

Monthly Crime KPIs read from https://Police.uk website and loaded from monthly files as below for example:  
#2018-07-metropolitan-street.csv
#2018-07-city-of-london-street.csv

Dwelling fires data for Londong at Easting,Northing (X,Y) coordinates which need to be transformed to Lat/Long and projected:
"https://assets.publishing.service.gov.uk/government/uploads/system/uploads/attachment_data/file/738425/domestic-appliance-fires-datatset.ods" </font>